---
title: "Analyses Pilot"
author: "Mora Maldonado"
date: "6/30/2017"
output: html_document
---

#TODO and comments
+ Include in this file rough predictions
+ Decide exclusion criteria (based on accuracy and time)
+ There seem to be no differences in time (maybe more time pressure?)
+ Stats won't work with this amount of subjects, specially given that we have to take subjects out. Also, just by eye there is nothing in the online data. 


##Charging packages
_[HIDDEN]_
```{r packages, include=FALSE}
library(tidyverse)
library(ggplot2)
library(lme4)
library(plyr)

# Standard error of the mean
se <- function(x, ...) {
  n <- length(x)
  return(sd(x, ...)/sqrt(n))
}
```
##Chargind data 
FYI: *data* contains all the results, *experimental_items* contains only results for experimental trials
```{r Charging data}
data <- read.csv("PilotResults.csv")
data <- data[!apply(is.na(data) | data == "", 1, all),]
info <- read.csv("PilotInfo.csv")
```

### Organizing a little bit
**Printing type of data in each column to check whether everything is right**
```{r Organizing data}
data$Subject <- factor(data$Subject)
data$Type <- factor(data$Type)
data$Condition <- factor(data$Condition)
data$Response <- factor(data$Response)
data$X <- factor(data$X)
data$Response.Numeric <- data$Response
levels(data$Response.Numeric) <- c(2,1,3,0)
data$Response.Numeric <- as.numeric(as.character(data$Response.Numeric))
data$Chunk.Time.Log <- log(data$Chunk.Time)
data$Total.Time.Log <- log(data$Total.Time )
data$Response.Time.Log <- log(data$Response.Time)
experimental_items <- subset(data, Type=='experimental_trial')
fillers<- subset(data, Type=='filler')


str(data)
```

## Plots
### Offline responses
Responses can go from **0** (Totally incomplete) to **3** (Totally complete). We transformed this into a continuous variable, measure the percentage of completeness

NB: Subject means will serve to exclude subjects that are very different. 
```{r Offiline results}
offline_data.subject<- aggregate(Response.Numeric~Subject+Condition, data= experimental_items, mean, na.rm=T)
ggplot(offline_data.subject, aes(y=Response.Numeric, x=Condition, colour=Subject, group=Subject, label=Subject)) + geom_point() + geom_line(alpha=.5) +geom_text(aes(label=Subject),hjust=0, vjust=0)

offline_data.overall<- ddply(offline_data.subject, c("Condition"),
                      function(offline_data.subject)c(response=mean(offline_data.subject$Response.Numeric, na.rm=T), se=se(offline_data.subject$Response.Numeric, na.rm=T)))

ggplot(offline_data.overall, aes(y=response, x=Condition, fill=Condition)) +
  geom_bar(position=position_dodge(), stat="identity")  +   
  ylab('Percentage of completeness') + 
  geom_errorbar(aes(ymin=response-se, ymax=response+se), width=.2, position=position_dodge(.9)) 


```

### Online response
#### Listening time per chunks in experimental items
NB: ROI = CHUNK 4 (and following given spill over)
```{r Online responses, fig.width=10}

online_data.subject<- aggregate(Chunk.Time.Log~Subject+Condition+X, data= experimental_items, mean, na.rm=T)

ggplot(online_data.subject, aes(y=Chunk.Time.Log, x=X, colour=Condition, group=Condition)) + 
  geom_point() +
  geom_line(alpha=.5) + 
  facet_grid(.~Subject) + 
  theme_minimal() +  
  ylab("Listening Time (Log)") +
  xlab("Chunk") 

online_data.overall<- ddply(online_data.subject, c("Condition", "X"),
                       function(online_data.subject)c(response=mean(online_data.subject$Chunk.Time.Log, na.rm=T), se=se(online_data.subject$Chunk.Time.Log , na.rm=T)))

ggplot(online_data.overall, aes(y=response, x=X, colour=Condition, group=Condition)) + 
  geom_point(size=3, shape=21, fill="white", alpha=.5) + 
  geom_line(alpha=.5) +  
  theme_minimal() +
  ggtitle('Listening time per chunk') +
  ylab("Listening Time (Log)") +
  xlab("Chunk") +
  geom_errorbar(aes(ymin=response-se, ymax=response+se), alpha=.4, width=.2)

```


#### Listening time per chunks in experimental items
NB: ROI = CHUNK 4 (and following given spill over)
```{r, fig.width=10}

online_data.subject<- aggregate(Chunk.Time~Subject+Condition+X, data= experimental_items, mean, na.rm=T)
online_data.overall<- ddply(online_data.subject, c("Condition", "X"),
                       function(online_data.subject)c(response=mean(online_data.subject$Chunk.Time, na.rm=T), se=se(online_data.subject$Chunk.Time , na.rm=T)))

ggplot(online_data.overall, aes(y=response, x=X, colour=Condition, group=Condition)) + 
  geom_point(size=3, shape=21, fill="white", alpha=.5) + 
  geom_line(alpha=.5) +  
  theme_minimal() +
  ggtitle('Listening time per chunk') +
  ylab("Listening Time (RAW)") +
  xlab("Chunk") +
  geom_errorbar(aes(ymin=response-se, ymax=response+se), alpha=.4, width=.2)

```



####  Listening time for fillers
NB: I don't remember how fillers were constructed, and I don't know where exactly are the out-of-key chords
*[PLEASE INSERT HERE DIFFERENCES BETWEEN CONDITIONS FOR FILLERS]*

```{r fig.width=10}

online_data.subject.fillers<- aggregate(Chunk.Time.Log~Subject+Condition+X, data= fillers, mean, na.rm=T)
ggplot(online_data.subject.fillers, aes(y=Chunk.Time.Log, x=X, colour=Condition, group=Condition)) + 
  geom_point() +
  geom_line(alpha=.5) +
  scale_colour_brewer(palette='Oranges') +
  ggtitle('Listening time in Fillers')+
  facet_grid(.~Subject) + 
  theme_minimal()

online_data.overall.fillers<- ddply(online_data.subject.fillers, c("Condition", "X"),
                            function(online_data.subject.fillers)c(response=mean(online_data.subject.fillers$Chunk.Time.Log, na.rm=T), se=se(online_data.subject.fillers$Chunk.Time.Log , na.rm=T)))

ggplot(online_data.overall.fillers, aes(y=response, x=X, colour=Condition, group=Condition)) + 
  geom_point(size=3, shape=21, fill="white") + 
  geom_line(alpha=.7) +  
  theme_minimal() +
  scale_color_brewer(palette='Oranges')+
  ggtitle('Listening time per chunk in Fillers') +
  ylab("Listening Time (Log)") +
  xlab("Chunk") +
  geom_errorbar(aes(ymin=response-se, ymax=response+se), alpha=.3, width=.2)

```

#### Total listening time
```{r}
online_data.subject_total <- aggregate(Total.Time.Log~Subject+Condition, data= experimental_items, mean, na.rm=T)
ggplot(online_data.subject_total, aes(y=Total.Time.Log, x=Condition, group=Subject, color=Subject)) + geom_point() + geom_line(alpha=.5) +  theme_minimal()

online_data.overall_total<- ddply(online_data.subject_total, c("Condition"),
                            function(online_data.subject_total)c(response=mean(online_data.subject_total$Total.Time.Log, na.rm=T), se=se(online_data.subject_total$Total.Time.Log , na.rm=T)))

ggplot(online_data.overall_total, aes(y=response, x=Condition, fill=Condition)) +
  geom_bar(position=position_dodge(), stat="identity")  +
  coord_cartesian(ylim=c(7.5, 9.3)) +
  geom_errorbar(aes(ymin=response-se, ymax=response+se), width=.2, position=position_dodge(.9))

```






